Region-network sparsity priors for\\ high-dimensional inference in fMRI data

### 2015-11-29 paper/paper.tex
new adventures

\def\B#1{\bm{#1}}
%\def\B#1{\mathbf{#1}}
\def\trans{\mathsf{T}}

@@

@@

@@

>>>>

\def\B#1{\bm{#1}}
%\def\B#1{\mathbf{#1}}
\def\trans{\mathsf{T}}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

data exhibit natural correlations between neighboring voxels forming clusters

@@

\paragraph{Numerical Optimization}

for every column u of U, it compute a column v of V solving

we aim at learning a weight vector w ∈ Rp and an intercept b ∈ R
such that the prediction of y can be based on the value of w⊤x + b.

We omit a bias term, since the data were mean-centered
and unit-variance scaled.
The scalar b is not particularly informative

however the vector w corresponds to a volume that
can be represented in brain space as a volume

more precisely, we denote by X ∈ Rn×p the design matrix
assembled from n fMRI volumes and by y ∈ Rn the corresponding n targets.
In other words, each row of X is a p-dimensional sample,
i.e., an activation map of p voxels related to one stimulus presentation.
for visualization of the predictive pattern of voxels.

Learning the parameters (w, b) remains challenging
since the number of features (104 to 105 voxels) exceeds
by far the number of samples (a few hundreds of volumes).

To address this issue, dimensionality reduction attempts to
find a low dimensional subspace that concentrates
as much of the predictive power of
the original set as possible for the problem at hand.
-> we do not want to do preliminary feature selection or
dimensionality reduction
or feature agglomeration because we want to fit one model parameter
to each brain voxel for maximal interpretability
This corresponds to discarding some columns of X.

\begin{equation}
  \argmin 0.5||u-v||_2^2 + \lambda\sum_{g \in T} \eta_g||v_g||_2
\end{equation}

@@

The same classification performance can be reached by
many different models -> we naturally want to priviledge those
among the equally performing models that are closest to
what we know about the brain

-> interpreta bility and accuracy typically exclude each other
(cf. Hastie)
